---
title: "Fitting A Linear Regression Model"
author: "Jeevan"
date: "12/06/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\section{AIM} 
\subsection{A rocket motor is manufactured by bonding together two types of propellants, an igniter and a sustainer. The shear strength of the bond (Y) is thought to be a linear function of the age of the propellant (X) when the motor is cast.
Fit a simple linear regression to the data that involving the following steps by using R.
a)	Plot the scatter diagram for the data .
b)	Estimate the parameters of a simple linear regression model.
c)	Obtain the fitted values of the model.
d)	Show that the sum of fitted values and sum of observed values of Y are equal.
e)	Obtain the residuals and show that the sum of residuals is zero.}

\section{PROCEDURE}
```{r}
library(readxl)
lab1 <- read_excel("C:/Users/Jeevan/Desktop/Christ University/Statistics/Linear Regression/lab1.xlsx")
View(lab1)
attach(lab1)
```
\subsection{The readxl library helps us in importing the excel sheet for our regression analysis.} 
```{r}
plot(age,sheer,main="Scatter Plot")
scatter.smooth(age,sheer,main = "Fitted Linear Scatter Plot")
```
The above figure shows a scatter plot for the data with a fitted linear regression model.
```{r}
model=lm(sheer~age)
model
```
Here we fit a linear model to the variables which gives us the slope intercept. 
```{r}
fit = fitted.values(model)
fit
```
\subsection{We then found the predicted values for the 20 entries in the dataset.} 
```{r}
res=resid(model)
sum(res)
sum(fit)
sum(sheer)
```
\subsection{The residuals have been found above and this tells us that the sum of fitted values and sum of observed values of Y are equal. Also the sum of residuals is zero.}